
To simplify working with the dispersion toolkit, the compiled binaries may be installed into a convenient directory. 

\paragraph{Linux Operating Systems: make}

In Linux Operating Systems, the default location depends on the distribution's configuration, which however is usually
\codeline{/usr/local}
but not always. Installing into this directory usually requires root access. Installation into the home directory of $\codef{user}$ with
\codeline{cmake .. -DCMAKE\_INSTALL\_PREFIX=/home/user/bin}
accomplishes this goal, while being in the build directory as discussed in the previous section on building this software. Installation with
\codeline{make install}
can be invoked after a successfull build.


\paragraph{Windows Operating Systems: Visual Studio}

In the Windows Operating Systems, using Visual Studio, installation into the default directory
\codeline{C:/Program Files (x86)/dispersion-toolkit}
requires administrator priviledges. In this matter, the powershell with elevated rights needs to be started, for instance with
\codeline{start-process powershell -verb runas}
or directly from the Windows File Explorer. With being in the previously created
\codeline{./dispersion-toolkit/build}
directory, the Visual Studio solution of this project is open with
\codeline{./dispersion-toolkit.sln}
in administrator mode. This situation can be confirmed by investigating the title bar of Visual Studio, now containing \enquote{Administrator}. Installation is accomplished with building the sub project
\codeline{INSTALL}
through right click on it while choosing \codef{Build}. After successful execution, the installation directory now contains the build executables within the
\codeline{C:/Program Files (x86)/dispersion-toolkit/bin}
directory.

A custom installation directory is set with
\codeline{CMAKE .. -DCMAKE\_INSTALL\_PREFIX="C:/dispersion-toolkit"}
which might not require administrator priviledges. The current install directory can be checked by opening \codef{CMakeCache.txt} and, therein, reading the line starting with
\codeline{CMAKE\_INSTALL\_PREFIX:PATH=}
upon which follows the actually used installation path.
