\documentclass[12pt,a4paper,refnotes]{extbook}

\input{preamble}
\input{mathsymbols}
\input{textsymbols}
\input{hyphenation}

\newcommand{\procarginseq}[1]{%
\begin{procarg}{--i=FILE | --i FILE}
  Retrieves a point set sequence of size $#1$ from \codef{FILE}, meaning a single point set. Its absence is substituted by stdin. The end of a point set, which equals the line \codef{\#eos}, starts the algorithm.
\end{procarg}}

\newcommand{\procargout}{%
\begin{procarg}{--o=FILE | --o FILE}
  Redirects the computed results to \codef{FILE}, opened in overwrite mode (not appending mode). Without \codef{FILE}, results are forwarded to stdout. Errors encountered during the  program’s execution are streamed into stderr, and not into either stdout or \codef{FILE}.
\end{procarg}}

\newcommand{\procargdelimiter}{%
\begin{procarg}{--delimiter=CHARACTER}
  Define a delimiter character to separate coordinates of a point in the resulting output. A usual \codef{CHARACTER} could be empty space (\codef{' '}) or tabular character (\codef{'\chartab'}), for instance.
\end{procarg}}

\newcommand{\procargsilent}{%
\begin{procarg}{--silent}
  Suppress comments in the output stream, yielding only the computed value. The latter could be the point set or its cardinality.
\end{procarg}}

\addbibresource{bibliography.bib}

%\makeatletter
\title{Dispersion toolkit documentation}
\author{The contributors}
\date{24. February 2021}

\begin{document}
\frontmatter
\maketitle
\input{acknowledgements}
\tableofcontents
\clearpage

\mainmatter
\chapterf{Introduction}{ch-intro}

\chapterf{Point sets and sequences}{ch-sets}
\sectionf{Fibonacci sets}{ch-sets-fibo}
\sectionf{Kritzinger's modified Fibonacci sets}{ch-sets-kritz}
\sectionf{Coordinate swapping}{ch-sets-cswap}

\input{ch-measures}
\input{ch-stat}
\input{ch-opt}
\input{ch-vis}
\input{ch-transduce}
\input{ch-credits}

\clearpage

\backmatter
\appendix
\printbibliography[heading=bibintoc]

\end{document}
